% Identifies root document to latex workshop:
% !TEX root = JoshBoothCoverLetter.tex

\input{setup/preamble.tex}
\input{setup/macros.tex}


\begin{document}

    \name{Josh Booth}{C/C++ Software Engineer}
    \receiver{Verge Aero}

    \para{Dear Hiring Manager,}
    \para{
        Verge Aero caught my attention due to it's unique fusion of engineering disciplines that when properly combined create awe-inspiring performances.
        You are operating on the cutting edge technology and I would love to be a part of creating a truly special product.
    }
    \para{
        My background is in embedded C/C++ development on various microcontrollers including PIC, AVR, STM32, and ESP32 MCUs.
        I currently work with a team creating drivers and microcontroller demonstrations for use by customers. This requires the code in the projects to have thorough documentation for easy adaptation by customers in their designs.        
        I also have experience designing system architecture for larger scale projects so each of the moving pieces seamlessly integrate by the end (see 3D PEEK Printer in my resume.)
    }
    \para{
        I have a strong interest in joining a team of other self-starting engineers whose talents and creativity will help me make a meaningful impact both in the company and in the tech space as a whole.
        With my track record of turning ideas into reality, I am confident that my skills and competitive nature aligns with the innovative spirit and drive Verge Aero needs.
    }
    \para{
        I hope to hear back from you soon.
    }
    \para{        
        Best, \\
        Josh
    }

    \bottom{Chandler, AZ}{(717) 494-6466}{boothjmail@gmail.com}
\end{document}
