\documentclass[12pt]{FreemanCV}

\graphicspath{{./images/}}

\columnratio{0.60, 0.40}

\begin{document}

\begin{paracol}{2}

\parbox[][0.05\textheight][c]{\linewidth}{ \centering {\sffamily\fontsize{35}{60}\selectfont Josh \textbf{Booth}} }

\switchcolumn

\parbox[top][0.1\textheight][c]{\linewidth}{ % Box to hold the colored box; change the fixed height as needed to match the box to the left
	\colorbox{shade}{ % Create colored box and specify background color
		\begin{supertabular}{@{\hspace{3pt}} p{0.05\linewidth} | p{0.775\linewidth}} % Start a table with two columns, the table will ensure everything is aligned
			\raisebox{-1pt}{\faPhone} & 1+ (717) 494-6466 \\ % Phone number
			\raisebox{-1pt}{\small\faEnvelope} & \href{mailto:boothjmail@gmail.com}{boothjmail@gmail.com} \\ % Email address
			\raisebox{-1pt}{\faHome} & Chandler, AZ \\ % Address
			\raisebox{-1pt}{\faLinkedinSquare} & \href{https://www.linkedin.com/in/joshua-f-booth/}{LinkedIn} \\ % LinkedIn profile
			% See fontawesome.pdf in the Fonts folder for all icons you can use
		\end{supertabular}
	}
	\vfill % Push content to the top of the box
}
\end{paracol}
\vspace{-35pt}

%---------------------------------------------------------------------------------------- % PROFESSIONAL SUMMARY %---------------------------------------------------------------------------------------- \section{Professional Summary} \begin{center} Technical Product Marketer and AI/ML Developer with expertise in machine learning, deep learning frameworks (PyTorch, TensorFlow), embedded systems, and developer engagement. Skilled in product demos, technical content creation, and leading technical marketing initiatives in AI and software stacks. \vspace{-7pt} \end{center}

%---------------------------------------------------------------------------------------- % WORK EXPERIENCE %----------------------------------------------------------------------------------------

\section{Relevant Work Experience}

\jobentry {Jun 2022 - Present} {FT} {Microchip Technology} {Technical Product Marketer}
{ \item Lead technical marketing expert for the latest 8-bit PIC microcontrollers and AI-driven product features. \item Created customer-facing application layers for AI and machine learning use cases, demonstrating product capabilities. \item Developed demos, code, and technical content for webinars and industry conferences to showcase AI product integrations. \item Organized marketing strategies for AI-driven peripherals (e.g., configurable logic blocks in the PIC16F131xx). \item Engaged with developer communities through social media, forums, and technical presentations. \item Led a social media analytics initiative improving impressions and CTR by 400\%. \item Identified and optimized customer journeys using AI tools to improve retention by 10\%. }

\jobentry {Jun 2017 - Jan 2022} {FT} {Naval Research Lab - Space Technology Division} {Machine Learning Researcher} { \item Designed supervised learning models for video streaming AI applications using PyTorch and TensorFlow. \item Optimized machine learning algorithms for deployment in remote environments with limited resources. \item Developed image preprocessing and feature extraction pipelines for AI video models. \item Created technical documentation and presented model performance results to technical and non-technical stakeholders. }

\jobentry {Sep 2016 - Jun 2022} {FT/PT} {Mark Oil and Gas LLC.} {Robotics Systems Engineer} { \item Developed robotics solutions integrating AI for mechanical simulations, automation, and image processing. \item Designed custom firmware and wiring for robotics control systems. \item Conducted hardware debugging and optimization for embedded AI systems. }

%---------------------------------------------------------------------------------------- % ENGINEERING PROJECTS %----------------------------------------------------------------------------------------

\vspace*{-10pt} \section{Sample Engineering Designs} { \vspace*{-7pt} \begin{itemize}[leftmargin=10pt] \item \href{https://github.com/jfcbooth/3dpp}{\linkcolor\scriptsize\faLink\normalcolor\normalsize\,\textbf{PEEK 3D Printer}} - AI-driven system for real-time thermal management and printing control. \item \href{https://github.com/microchip-pic-avr-examples/pic16f56q71-audio-light-show-mplab-mcc}{\linkcolor\scriptsize\faLink\normalcolor\normalsize\,\textbf{DMX Audio Visualizer}} - Embedded AI for dynamic visual effects. \item \href{https://github.com/jfcbooth/security_system}{\linkcolor\scriptsize\faLink\normalcolor\normalsize\,\textbf{AI-Driven Security System}} - Security system integrating computer vision and ML for real-time threat detection. \end{itemize} }

%---------------------------------------------------------------------------------------- % EDUCATION %---------------------------------------------------------------------------------------- \section{Education} \textbf{B.S. in Computer Engineering; Mathematics minor}\ \small\textsc{Summa Cum Laude; 3.98 GPA; CMPE 322/120 Supplemental Instructor}\ \textit{Shippensburg University of Pennsylvania}

%---------------------------------------------------------------------------------------- % COMPETENCIES %----------------------------------------------------------------------------------------

\section{Competencies} \begin{itemize}[leftmargin=10pt] \itemsep-5pt \item \textbf{AI/ML Tools:} Python, TensorFlow, PyTorch, TFLearn \item \textbf{Software:} C, Python, Linux, Marlin, Bash, Embedded Development, Fusion 360, KiCAD, Eagle, MPLAB X, XC8 \item \textbf{Hardware:} Circuit Design, Programmable Logic, PIC and AVR Microcontrollers, EDA tools \item \textbf{Personal Interests:} Chess, Piano, Track and Field, Rugby, Rock Climbing, Valorant \end{itemize}

\vfill \vspace{1cm} \end{document}