% Identifies root document to latex workshop:
% !TEX root = JoshBoothCoverLetter.tex

\input{setup/preamble.tex}
\input{setup/macros.tex}


\begin{document}

    \name{Josh Booth}{C/C++ Software Engineer}
    \receiver{Verge Aero}

    \para{Dear Hiring Manager,}
    \para{
        Verge Aero caught my attention due to its unique fusion of engineering disciplines that when properly combined create awe-inspiring performances.
        You are pioneering a new industry, and I would love to be part of creating a truly special product.
    }
    \para{
        My background is in embedded C/C++ development on various microcontrollers including PIC, AVR, STM32, and ESP32 MCUs.
        I currently work with a team creating drivers and demos for PIC and AVR MCUs to be used by customers. This requires the code in the projects to have thorough documentation for easy adaptation by customers in their designs.        
        I also have experience designing hardware system architecture for large-scale projects so each of the moving pieces is able to seamlessly integrate (see 3D PEEK Printer in my resume.)
    }
    \para{
        I have a strong interest in joining a team of other self-starting engineers whose talents and creativity will help me make a meaningful impact both in the company and in the tech space as a whole.
        With my track record of turning ideas into reality, I am confident that my skills and competitive nature align with the innovative spirit and drive Verge Aero needs.
    }
    \para{
        I hope to hear back from you soon.
    }
    \para{        
        Best, \\
        Josh
    }

    \bottom{Chandler, AZ}{(717) 494-6466}{boothjmail@gmail.com}
\end{document}
